---
title: "Data Wrangling Exercise 5"
author: "Danielle J. Navarro"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Yet another exercise in fixing broken code, but this time using the frames data!

```{r, packageload, error=TRUE, message=FALSE}
library(tidyverse)
library(here)
library(skimr)
frames <- here("analysis", "data", "frames_ex2.csv") %>% read_csv()
```


Print and skim the data. Notice that there are a lot of rows, because every row is a single judgment!

```{r explore, error=TRUE}
frames
skim(frames)
```

Use filter to extract the data from person with `id` of 12.

```{r filterone, error=TRUE}
one_person <- frames %>% 
  filter(id == 12)
```

Inspect their raw data:

```{r inspectone, error=TRUE}
one_person
```

Next let's look at their average "response" across each of the 7 test items (i.e., group by test item and compute the mean response for each item.

```{r generalisation, error=TRUE}
generalisation <- one_person %>%
  group_by(test_item) %>%
  summarise(mean_response = mean(response))
```

Finally, as a reward, a picture! This code shold start working once the chunks above work

```{r picture, error=TRUE}
generalisation %>% 
  ggplot(aes(x = test_item, y = mean_response)) +
  geom_point() + 
  geom_smooth(method = lm)
```



