---
title: "Data Wrangling Exercise 6"
author: "Danielle J. Navarro"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, packageload, error=TRUE, message=FALSE}
library(tidyverse)
library(here)
tidy_nails <- here("analysis", "data", "tidy_nails.csv") %>% read_csv()
tidy_nails
```

The data come from market research reported by [Nails Magazine](www.nailsmag.com/page/70218/market-research), tracking the number of nail salons and technicians working in said salons, across all U.S. states over several years. 

## Gather

Use the `gather()` function to create a long form data frame in which there are two variables, `measure` (which could be either "technicians" or "salns") and `count`, which is indicates the numnber of technicians/salons, and then arrange it by U.S. state and year.

```{r gather, error=TRUE}
long_nails <- tidy_nails %>%
  gather( YOUR-CODE-HERE )  %>% 
  arrange( YOUR-CODE-HERE )

print(long_nails)
```

## Spread

Add a code chunk below that spreads the data out again
