---
title: "Data Wrangling Exercise 2"
author: "Danielle J. Navarro"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packageload, message=FALSE}
library(tidyverse)
```

The second DIY exercise is about the pipe operator `%>%`. In the code below, I've written a some code that generates random numbers and then calculates the mean. First, let's decide on how many numbers:

```{r}
N <- 100
```

Here is the nonpiped version of the code:

```{r traditionalcode1, error=TRUE}
mean(rnorm(N))
```

In the code chunk below, write a piped version of the same thing:

```{r pipedcode1, error=TRUE}
N %>% rnorm() %>% mean()
```

By default, the pipe operator assumes that the inpit takes the place of the *first* argument in the function. So let's suppose I want to calculate the 20% trimmed mean, of normally distributed numbers with mean 100 and standard deviation 15. Here's the traditional version:

```{r traditionalcode2, error=TRUE}
mean(
  rnorm(N, mean = 100, sd = 15),
  trim = .2
  )
```

Can you rewrite this in piped form? What do you notice?

```{r pipedcode2, error=TRUE}
N  %>% 
  rnorm(mean = 100, sd = 15) %>% 
  mean(trim = .2)
```

It's cleaner, right? It's visually clearer how the different arguments are related to each other
