---
title: "Data Wrangling Exercise 3"
author: "Danielle J. Navarro"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Another exercise in fixing broken code!

```{r, packageload, error=TRUE, message=FALSE}
library(tidyverse)
library(here)
```

```{r loaddata, error=TRUE}
tidy_users <- here("analysis", "data", "tidy_users.csv") %>% read_csv()
```

In this first section what we're aiming to do is summarise (count) the total number of users in every month, and store it in a variable called `total_users`

```{r monthlydata, error=TRUE}
monthly_users <- tidy_users %>%
  group_by( Month ) %>%
  summarise(
    total_users = sum( Users ) 
  ) %>%
  ungroup()
```

The output from the previous chunk should be a data set (a tibble). Modify the code below so that it prints out that variable:

```{r monthlydata2, error=TRUE}
monthly_users
```

Here is some code that will draw a pretty picture once the code above is working. You shouldn't need to edit this at all!

```{r picture, error=TRUE}
monthly_users %>% 
  ggplot(aes(x = Month, y = total_users)) + 
  geom_col() 
```

As a bonus exercise, go back to the `monthly_users` chunk above and fix it so that we `ungroup()` the summarised data.

