---
title: "Data Wrangling Exercise 4"
author: "Danielle J. Navarro"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Another exercise in fixing broken code!

```{r, packageload, error=TRUE, message=FALSE}
library(tidyverse)
library(here)
tidy_users <- here("analysis", "data", "tidy_users.csv") %>% read_csv()
tidy_users
```

## Problem 1... 

- 1a: Filter the data so that we only retain rows for dates with more than 200 users
- 1b: Select the Date and Users variables only
- 1c: Arrange the output to sort the rows by User, in descending order (hint: there is a function called `desc()`)

```{r problem1, error=TRUE}
output1 <- tidy_users %>% 
  filter( Users > 200 ) %>% 
  select( Date, Users ) %>%
  arrange( desc(Users) )

print(output1)
```

## Problem 2...

Apply a `filter` to the data so that we only include data from Saturdays with more than 50 users; and `arrange` the output so that cases are arranged by number of users.

```{r problem2, error=TRUE}
output2 <- tidy_users %>% 
  filter(Weekday == "Saturday" & Users > 50) %>%
  arrange(desc(Users))

print(output2)
```


## Problem 3...

Create a sorted table. Use `group_by` and `summarise` to calculate the average number of users for every day of the week (including weekends!), and then use `arrange` to sort the weekdays by mean number of users. 

```{r problem3, error=TRUE}
output3 <- tidy_users %>%
  group_by( Weekday ) %>%
  summarise( mean_users = mean(Users) ) %>% 
  arrange( mean_users )

print(output3)
```

## Problem 4...

Take the results from `output3` and use `mutate()` to round the `mean_users` to the nearest whole number (there is a function called `round()`) 

```{r problem4, error=TRUE}
output4 <- output3 %>%
  mutate(mean_users = round(mean_users))

print(output4)
```




